---
title: "ST558 Project 2"
author: "Zack Vaskalis"
date: "07/03/2020"
output: 
  rmarkdown::github_document:
    toc: TRUE
    toc_depth: 3
    html_preview: TRUE
urlcolor: blue
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

This project uses the Online News Popularity Data Set which can be found at the University of California Irvine [UCI Machine Learning Repository, Center for Machine Learning and Intelligent Systems](https://archive.ics.uci.edu/ml/datasets/Online+News+Popularity#). The dataset being used here was compiled by several researchers in Portugal, who collected articles from [Mashable](www.mashable.com) and compiled associated statistics for a period of two years, with the goal of being able to predict the number of shares in social networks (a measure of popularity). The dataset has over 39,000 records of information spanning the two year time period from January 07, 2013 to December 27th, 2014.  The dataset also contains 61 variables, of which 58 are predictive attributes, 2 non-predictive variables(the source url and the time between article publication and dataset acquisition), and finally the goal field for prediction: the number of shares.

## Including Code   

You can include R code in the document as follows:   

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.