---
title: "Weekday"
author: "Zack Vaskalis"
date: "07/03/2020"
output: 
  rmarkdown::github_document:
    toc: TRUE
    toc_depth: 3
    html_preview: TRUE
urlcolor: blue
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This project uses, for analysis, the Online News Popularity Data Set which can be found at the University of California Irvine [UCI Machine Learning Repository, Center for Machine Learning and Intelligent Systems](https://archive.ics.uci.edu/ml/datasets/Online+News+Popularity#). The dataset being used here was compiled by several researchers in Portugal, who collected articles from [Mashable](www.mashable.com) and compiled associated statistics for a period of two years, with the goal of being able to predict the number of shares in social networks (a measure of popularity). The dataset has over 39,000 records of information spanning the two year time period from January 07, 2013 to December 27th, 2014.  The dataset also contains 61 variables, of which 58 are predictive attributes, 2 non-predictive variables(the source url and the time between article publication and dataset acquisition), and finally the goal field for prediction: the number of shares.

### Information on Attributes for Analysis:

Out of the 61 Attributes available in this dataset for analysis, in order not to overfit the model with too many dependent variables (which could yield not enough generalization of the dataset to make predictions, especially valid ones), I have chosen to use the following 7 variables, 6 which are predictive, and 1, the shares variable, which is outcome variable.  The weekday variables are also included, but only for subsetting the data by the day of the week.  Once we have the "Monday" dataset, for instance, all of these `weekday_is_*` variables will be removed from the dataset.  The variables selected are below, and the reasoning behind their selection follows.

Attribute Information:    
1.  n_tokens_content: Number of words in the content    
2.  n_unique_tokens: Rate of unique words in the content    
3.  average_token_length: Average length of the words in the content    
4.  global_subjectivity: Text subjectivity    
5.  rate_positive_words: Rate of positive words among non-neutral tokens    
6.  avg_positive_polarity: Avg. polarity of positive words    
7.  shares: Number of shares (target outcome trying to predict)    
8.  weekday_is_variables: Was the article published on a _______?    

*  weekday_is_monday: Was the article published on a Monday?    
*  weekday_is_tuesday: Was the article published on a Tuesday?    
*  weekday_is_wednesday: Was the article published on a Wednesday?    
*  weekday_is_thursday: Was the article published on a Thursday?    
*  weekday_is_friday: Was the article published on a Friday?    
*  weekday_is_saturday: Was the article published on a Saturday?    
*  weekday_is_sunday: Was the article published on a Sunday?    




```{r loadlibraries, echo=TRUE, results=FALSE, warning=FALSE, comment=FALSE, message=FALSE}
#load necessary libraries
library(rmarkdown)
library(tidyverse)
library(caret)
library(lattice)
library(ggplot2)
library(dplyr)
library(haven)
library(rgl)
library(knitr)
library(tree)
library(randomForest)
library(psych)
library(DT)
library(summarytools)
```

## Data

```{r readInOnlineNewsPopularityDataset, echo=TRUE, message=FALSE, warning=FALSE}
# Read-in entire dataset
path <- "C:/Users/Zachary Vaskalis/Dropbox/ST558/OnlineNewsPopularity.csv"
weekdayDataRAW <- read_csv(path)

# Select only variables I am choosing to use for the analysis.
weekdayData1 <- select(weekdayDataRAW, n_tokens_content, n_unique_tokens,
                       average_token_length, weekday_is_monday, weekday_is_tuesday,
                       weekday_is_wednesday, weekday_is_thursday, weekday_is_friday,
                       weekday_is_saturday, weekday_is_sunday, global_subjectivity,
                       rate_positive_words, avg_positive_polarity, shares)

# Select only the specific day of the week I am interested in.
weekdayData2 <- filter(weekdayData1, weekday_is_monday == 1)

# Now we know we only have the day of the week filtered by above.
# So, we can remove all of the weekday_is_* variables now as they are no longer needed.
# Additionally, these variables are constant.  The selected weekday would contain all 1s,
# while the other weekdays are all 0s.  Thus, they are no longer useful for analysis.
weekdayData3 <- select(weekdayData2, -(weekday_is_monday:weekday_is_sunday))

```


```{r createTrainTestSets, echo=TRUE, message=FALSE, warning=FALSE}
# Get random number from the computer clock using Sys.time()
initial_seed <- Sys.time()
initial_seed <- as.integer(initial_seed)
print (initial_seed)
seed <- initial_seed %% 100000
#print(seed)

# -----------------RUN FROM HERE NOW THAT YOU HAVE RANDOM SEED-------------------------
# For reproducability, set seed using outcome of above process:
set.seed(42131)

# Get random sample of row numbers from large dataset to split data into train and test:
# 70% of data for training
train <- sample(1:nrow(weekdayData3), size = nrow(weekdayData3)*.70) 
# 30% of data for testing
test <- dplyr::setdiff(1:nrow(weekdayData3), train)

# Subset the Data into training and testing sets, using rows from train and test:
trainingData <- weekdayData3[train,]
testingData <- weekdayData3[test,]
```



## Summarizations

The summaries below are related to the training dataset.  The table that appears below is a summary of all of the variables from the training dataset using the `describeBy()` function from the `psych` package.

```{r summaryStatistics, echo=TRUE, message=FALSE, warning=FALSE}
# Summary statistics for all variables in the training dataset using the
# describeBy() function from the psych package
summaryData <- psych::describeBy(trainingData, trainingData$type)

x <- tibble(row.names(summaryData), summaryData) 
colnames(x)[1] <- "variable"
x[,4:10] <- round(x[,4:10],4)
y <- select(x,1,3,4,5,6,8,9,10)
datatable(arrange(y,desc(variable)))

#histogram(trainingData$n_tokens_content)
#plot(trainingData$n_tokens_content,trainingData$shares)
#plot(trainingData$n_tokens_title,trainingData$shares)
#plot(trainingData$n_unique_tokens,trainingData$shares)
#plot(trainingData$global_subjectivity,trainingData$shares)


#trainingData$n_tokens_content <- log(trainingData$n_tokens_content + 1)
#trainingData$shares <- log(trainingData$shares + 1)

#trainingData <- filter(trainingData, n_tokens_content > 0)

```

## Modeling

```{r linearModel, echo=TRUE, message=FALSE, warning=FALSE}
# Multiple Regression Model chosen using all 20 predictor variables to try to predict
# shares.  This will also allow for comparison to the random forest model, and RMSE 
# values will be compared between the two models.

mlr1 <- lm(shares ~ ., data = trainingData)
summary(mlr1)

trCtrl <- trainControl(method = "cv", number = 10)
mlr2 <- train(shares~., data=trainingData, method="lm",metric = "RMSE", trControl=trCtrl)
mlr2


```

The non-linear model chosen for this project is the random forests model.  This model is a good fit for this dataset given the number of predictors included for analysis.  In the model, a random subset of predictors is selected, which will allow for a good predictor to not dominate the tree fits.  We will specify `mtry` to have a value of `p/3`.

```{r nonLinearModel, echo=TRUE, message=FALSE, warning=FALSE}
# Non-linear model chosen is Random Forests Model  

# Model fit with training data
#rfFit <- randomForest(shares ~ ., data = trainingData, mtry = ncol(trainingData)/3,
#                     importance = TRUE)
# Fit Random Forest Tree using method = "rf" and tuning parameter, mtry
#trCtrl <- trainControl(method = "cv", number = 3)
#randFrst <- train(shares~., data = trainingData, method = "rf", trControl = trCtrl)
#randFrst


# Model predictions using testing data
#rfPred <- predict(rfFit, newdata = dplyr::select(testingData, -shares))

# Get the root mean squared error (RMSE) value - root of test prediction error

#rfRMSE <- sqrt(mean((rfPred-testingData$shares)^2))
#rfRMSE

```





